### 2016-12-06 paper/chapters/introduction.tex
modify introduction

\section{Introduction}
\label{sec:motivation}
Generative models have been proposed as one of the most promising approaches towards
learning representations of real world data by some of the leading researches (YannLeCun, OpenAI blogpost).

In recent years supervised learning has yielded impressive results,
however for these models to suceed huge amount of labelled data is needed.
Unsupervised learning, that is learning from unlabelled data, has been expressed
as one hurdles toward general articial intelligence (citation needed).
Early approaches toward this problem however have shown that these problems are very hard to learn (intractable?).

In generative models the approach is different in a way that
we search for a good internal representation of the data.
This resembles the way humans learn about the world where we incrementally build
a model of the world.

>>>>

\section{Introduction}
\label{sec:introduction}
Generative models are one of the most promising ways to perform unsupervised learning (citation needed).
More specifically, generative modelling assumes a hidden structure $z$ explaining the input data $x$.
This assumption is reasonable given the following examples:\\

\begin{itemize}
  \item \textbf{Images} often have multiple thousands of dimensions, but the underlying structure is often far simpler. For example are 28x28 images of handwritten digits 784-dimensional but assuming one-hot encoding the most important information - the digit - it can be explained using 10 dimensions. There are a few more dimensions, stroke width, cursive, position, size. But still far lower than 784. We will take a look at this example later on in \ref{sec:vae}.
  \item \textbf{Speech} or more precisely the recording of it is high-dimensional, while the information it carries (the spoken words) can be represented in a low-dimensional space.
  \item \textbf{...}
\end{itemize}

After a short overview of different approaches and methods and an introductory example with the sigmoid belief net (SBN), we will take a closer look at two promising frameworks, the variational autoencoder (VAE) and the generative adversarial network (GAN)

%Generative models have been proposed as one of the most promising approaches towards
%learning representations of real world data by some of the leading researchers (YannLeCun, OpenAI blogpost).

%In recent years supervised learning has yielded impressive results,
%however for these models to succeed huge amount of labelled data is needed.
%Unsupervised learning, that is learning from unlabelled data, has been expressed
%as one hurdles toward general articial intelligence (citation needed).
%Early approaches toward this problem however have shown that these problems are very hard to learn (intractable?).

%In generative models the approach is different in a way that
%we search for a good internal representation of the data.
%This resembles the way humans learn about the world where we incrementally build
%a model of the world.
